---
title: "p8105_hw1_nl2835"
author: "Nancy Le"
date: 09-21-2023
output: github_document
---

Problem #1

```{r}
library(moderndive)
data("early_january_weather")
```

The "early_january_weather dataset describes hourly meteorological data for LGA, JFK, and EWR for the month of January 2013. This is a subset of the weather data frame from nycflights13. 

The format of this dataset is a dataframe of ``r nrow(early_january_weather)`` rows and ``r ncol(early_january_weather)`` columns representing hourly measurements and 15 variables. Some important variables are origin (meaning the weather station), year, month, day, hour, temp, and dewp. 

```{r}
mean_temp <- mean(early_january_weather[["temp"]])
```

The mean temperature is ``r mean_temp``.



```{r yx_scatter}
library(ggplot2)

ggplot(data = early_january_weather, aes(x = hour, y = temp, color = humid)) + geom_point()

```

```{r, echo = FALSE}
ggsave("temp_scatterplot.png")
```

Problem #2
```{r, echo = FALSE}
library(tidyverse)
```


```{r}
set.seed(1234)

hw_df = #create example data frame
  tibble( 
    random_sample = rnorm(10),
    vec_char = c("Hi", "I", "am", "making", "a", "character", "vector", "of", "length", "ten"),
    vec_logical = random_sample > 0, 
    vec_factor = factor(c("single", "married", "married", "single", "single", "divorced", "divorced", "single", "married", "married"))
  )
```

This is a data frame comprised of:
* a random sample of size 10 from a standard normal distribution
* a logical vector indicating whether elements from the random sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor "levels" of "single", "married", and "divorced"


```{r}
mean(pull, hw_df, vec_char)
```


```{r}
mean(pull, hw_df, vec_logical)
```

```{r}
mean(pull, hw_df, vec_factor)
```

The arguments to get the means of the logical, character, and factor vector are not numeric or logical, and returns NA. 
